Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-18 doc/JFLA2022/paper.tex
qualify coq-community to be about open source packages/projects

\subsection{Vision}
The \Hydras project, part of \community on GitHub~\cite{CoqCommunity}, aims to be an experimental platform for the collaborative development of documented libraries of formal proofs. \community is a community organization that the first and last authors founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting \coq packages, and working collaboratively on documentation projects. The \Hydras project demonstrates that these two goals are not independent: interesting \coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of the former Cantor and Additions libraries~\cite{CantorContrib,AdditionsContrib} (under the new names of Hydra-battles and Addition-chains), the Ackermann sub-library extracted from Russel O'Connor's Goedel library~\cite{OConnor05, Goedel}, and a bridge to the \gaia library by José Grimm~\cite{Gaia,grimm:hal-00911710}.
%
By following this approach of commenting interesting \coq packages, we provide new documentation content that contributes to the diversity of the thriving \coq ecosystem.

@@

\community is an informal organization run by volunteer Coq users on GitHub that aims to maintain interesting Coq projects for the long term and facilitate collaboration among Coq users on documentation, tooling, etc. \community was created in 2018, inspired by the {Elm Community} organization~\cite{zimmermann:tel-02451322}.
%
Such ``Community Package Maintenance Organizations'' exist in many software ecosystems, as they avoid the common problem of an important package becoming unmaintained after its author has moved on to other projects or has disappeared~\cite{zimmermann2021grounded}.

>>>>

\subsection{Vision}
The \Hydras project, part of \community on GitHub~\cite{CoqCommunity}, aims to be an experimental platform for the collaborative development of documented libraries of formal proofs. \community is a community organization that the first and last authors founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting open source \coq packages, and working collaboratively on documentation projects. The \Hydras project demonstrates that these two goals are not independent: interesting \coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of the former Cantor and Additions libraries~\cite{CantorContrib,AdditionsContrib} (under the new names of Hydra-battles and Addition-chains), the Ackermann sub-library extracted from Russel O'Connor's Goedel library~\cite{OConnor05, Goedel}, and a bridge to the \gaia library by José Grimm~\cite{Gaia,grimm:hal-00911710}.
%
By following this approach of commenting interesting \coq packages, we provide new documentation content that contributes to the diversity of the thriving \coq ecosystem.

@@

\community is an informal organization run by volunteer Coq users on GitHub that aims to maintain interesting open source Coq projects for the long term and facilitate collaboration among Coq users on documentation, tooling, etc. \community was created in 2018, inspired by the {Elm Community} organization~\cite{zimmermann:tel-02451322}.
%
Such ``Community Package Maintenance Organizations'' exist in many software ecosystems, as they avoid the common problem of an important package becoming unmaintained after its author has moved on to other projects or has disappeared~\cite{zimmermann2021grounded}.
